Toolset for an automated troubleshooting in SDNs

### 2013-11-05 draft.tex
concl

\begin{figure}
\centering
\includegraphics[scale=0.60]{layers.png}
\label{layers}
\caption{SDN architecture\label{layers}\protect\footnotemark}
\end{figure}
\footnotetext{Source : \cite{Heller:2013:LSL:2491185.2491197}}
\section{Network Troubleshooting - Tools}
\label{Network Troubleshooting - Tools}
\subsection{Network Debugger (NDB)}
SDNs bring a new way of building networks: like a programmer build a software, a network administrator will be able to program its network. The software programmer has tools to debug its program, like the well-known GDB.\\
NDB is a tool inspired from GDB, it aims at finding network error by identifying incorrect sequence of events. NDB has the ability to do a sort of \textit{breakpoint}, which is in fact a packet filter. When packet are matched by this filter, the breakpoint is triggered and the entire trace of that packet is displayed. The authors mention that the term \textit{tracepoint} should be more appropriate but the term \textit{breakpoint} is more familiar. NDB uses its \textit{backtrace} primitive to show the sequence of events for a packet. This trace is simply the sequence of forwarding actions applied on the packet by the switches through which it passed. For example of NDB utilisation, please refer to its paper \cite{ndb_paper}.\\
In our layering SDN architecture, NDB give us the opportunity to build a tool to confirm the right action of the policies implemented in the control application. For example, if a routing bug occurs in the network, a tool of top of NDB could observe paths taken by packets and complete switches states in order to conclude if the policies are correctly matched or not. If the policies are correctly matched, it means that the network administrator has written policies that dont't fit his needs. In this case, NDB has found the \textit{code layer} where the issue happen. Now if the policies are not correctly matched, then the issue does not come from an incorrect implementation. NDB has thus exclude the implementation to be the root of the bug and the search can continue among other layers, with other tools such as SOFT\cite{SOFT}.

@@

This paper has been dedicated to troubleshooting tools in Software-Defined-Network. The methodology used to present them is inspired from the layered architecture of the SDN stack, where each tool has a role to play in at least one layer. From the definition of the different layers, we have introduced tools which aims to find the incoherence between two \textit{state layer}. We introduced a Network Debugger (NDB) designed to find incoherences between policies and their effects. VeriFlow aims at verify invariant between the policy and the Device State. VeryFlow does some model checking technics between the SDN controller and the switches.\\
We also have introduced tools used to find the bug when the incoherence between two \textit{state layer} is identified. These tools operate inside the \textit{code layer} which is for recall, the implementation logic to maintain the mapping between two \textit{state layer}. These tools introduced are SOFT and NICE. SOFT acts on the Physical View and identify incoherence in the OpenFlow implementation between switches of different constructors. NICE can acts either on the controller software or in the switch firmware, it depends where the inconsistency is found by an other tools. \\
The main idea of this paper was to bring an overview of troubleshooting tools in SDNs and how they can works together. As we have explained, thanks to SDN stack, the job can be easily split and several tools can be used together to spot bugs.

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.60]{layers.png}
\label{layers}
\caption{SDN architecture\protect\footnotemark}
\end{figure}
\footnotetext{Source : \cite{Heller:2013:LSL:2491185.2491197}}
\section{Network Troubleshooting - Tools}
\label{Network Troubleshooting - Tools}
\subsection{Network Debugger (NDB)}
SDNs bring a new way of building networks: like a programmer build a software, a network administrator will be able to program its network. The software programmer has tools to debug its program, like the well-known GDB.\\
NDB is a tool inspired from GDB, it aims at finding network error by identifying incorrect sequence of events. NDB has the ability to do a sort of \textit{breakpoint}, which is in fact a packet filter. When packet are matched by this filter, the breakpoint is triggered and the entire trace of that packet is displayed. The authors mention that the term \textit{tracepoint} should be more appropriate but the term \textit{breakpoint} is more familiar. NDB uses its \textit{backtrace} primitive to show the sequence of events for a packet. This trace is simply the sequence of forwarding actions applied on the packet by the switches through which it passed. For example of NDB utilisation, please refer to its paper \cite{ndb_paper}.\\
In our layering SDN architecture, NDB give us the opportunity to build a tool to confirm the right action of the policies implemented in the control application. For example, if a routing bug occurs in the network, a tool of top of NDB could observe paths taken by packets and complete switches states in order to conclude if the policies are correctly matched or not. If the policies are correctly matched, it means that the network administrator has written policies that dont't fit his needs. In this case, NDB has found the \textit{code layer} where the issue happen. Now if the policies are not correctly matched, then the issue does not come from an incorrect implementation. NDB has thus exclude the implementation to be the root of the bug and the search can continue among other layers, with other tools such as SOFT\cite{SOFT}.

@@

This paper has been dedicated to troubleshooting tools in Software-Defined-Network. The methodology used to present them is inspired from the layered architecture of the SDN stack, where each tool has a role to play in at least one layer. From the definition of the different layers, we have introduced tools which aims to find the incoherence between two \textit{state layer}. We introduced a Network Debugger (NDB) designed to find incoherences between policies and their effects. VeriFlow aims at verify invariant between the policy and the Device State. VeryFlow does some model checking technics between the SDN controller and the switches. SOFT and FlowChecker cover the mapping between Device State and Hardware, both of multiple switches in the network. \\
We also have introduced tools used to find the bug when the incoherence between two \textit{state layer} is identified. These tools operate inside the \textit{code layer} which is for recall, the implementation logic to maintain the mapping between two \textit{state layer}. These tools introduced are SOFT and NICE. SOFT acts on the Physical View and identify incoherence in the OpenFlow implementation between switches of different constructors. NICE can acts either on the controller software or in the switch firmware, it depends where the inconsistency is found by an other tools. \\
The main idea of this paper was to bring an overview of troubleshooting tools in SDNs and how they can works together. As we have explained, thanks to SDN stack, the job can be easily split and several tools can be used together to spot bugs.
